### 2018-08-08 paper/approach.tex
up

To present the different parts of \name in detail, 
we align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They characterize anonymous communication protocols using the following 
categories: (i) \textit{network structure}, (ii) \textit{routing information},
(iii) \textit{communication model} and (iv) \textit{performance} (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}).

>>>>

To present the different parts of \name in detail, 
we align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They characterize anonymous communication protocols using the following 
categories: (i) \textit{network structure}%~\ding{168}
, (ii) \textit{routing information}%~\ding{169}
, (iii) \textit{communication model}%~\ding{170}
, and (iv) \textit{performance}%~\ding{171}
~(see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}).
